Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
wording
discuss about depth

@@

\begin{table}[tbh]
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
\hline
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\end{tabular}
\caption{TODO \textcolor{red}{version simple!!}}
\label{tab:tab3}
\end{table}

>>>>

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance increases with deeper trees. The reason is twofold. First, the deeper the tree, the larger is the conditioning. As it was observed in the comparison between correlation and partial correlation, it screens indirect links in the infered network. Second, the number of trees when trees are small need to be much higher in order to correctly estimate all pairs. However, as suggested by \cite{Gilles2014understanding}, limiting the maximal depth of trees may help to reduce the misestimation bias in variable importance comuting, i.e. infering the strengh of a link.

@@

\begin{table}[tbh]
\centering
\small
\begin{tabular}{@{}l *{8}{c}@{}}
\hline
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
%Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\end{tabular}
\caption{TODO \textcolor{red}{version simple!!}}
\label{tab:tab3}
\end{table}
